\subsubsection[Pin Types]{Pin Types\texorpdfstring{\protect\sechypt{sec_pintypes}{}}{}}
\label{sec:pintypes}

In this section the radial parameters of each of the pincell types used in the
fuel assemblies are detailed. Each of these describes a complete pincell
surrounded by the main coolant - in other words, the outer guide tube shell that
surrounds instrument tubes, control rods, and burnable absorber rods is
presented here as part of those pincells.

While the following radial parameters are constant throughout the axial extent
of the core of most pins, a distinction is made for the pins that have
components below the control rod stop at the bottom of the core. This region,
referred to as the ``dashpot'', consists of a tapering of the guide tubes to a
thinner radius that causes the constriction of flow to naturally prevent control
rods from extending too far into the core. In this model, this is approximated
by a region of thinner guide tubes (described further in later sections). Thus
radial parameters are provided for pins for both regions where appropriate. Note
that the central guide tubes of each assembly (the "instrument tubes") do not
shrink for the dashpot.

For all figures in this section, dimensions and materials are specified in order
starting from the inner region, through the outer rings. No thermal expansion is
considered.

\input{./specifications/pin/fuel}
\input{./specifications/pin/guidetube}
\input{./specifications/pin/instr}
\input{./specifications/pin/ba}
\input{./specifications/pin/cr}
